curacao_threeplayers_rest_monster

### 2023-10-30 inst/curacao1962_threeplayers_rest_monster.Rmd
typo
label all chunks

```{r}
library("hyper2")

@@

```{r}
  players <- 
    c("Petrosian", "Keres", "Geller", "Fischer", "Korchnoi",
      "Benko", "Tal", "Filip")
  names(players) <-   # accused of collusion or not
    c("coll", "coll", "coll", "USA", "USSR", "USA", "USSR", "TCH")
collusive_players <-     c("Petrosian", "Keres", "Geller")
 ```

@@

```{r}
cumulative_games
cumulative_collusive_games
cumulative_noncollusive_games
```

@@

```{r}
diff <- a$cncmp_white-a$cncmp_black  # difference in each game
table(diff)
table(abs(diff))
cumsum(table(abs(diff)))
```

@@

```{r}
table(a[,3],a[,5]-a[,6])
```

Then Fisher test:
```{r}
b <- subset(a,a[,5] != a[,6])
b <- subset(b,abs(b[,5]-b[,6])>1)
b <- subset(b,b[,3] != "1/2-1/2")
b <- cbind(b,white_rested = b[,5] < b[,6])
b

@@

```{r}
problem <- function(...){stop("must be a white win or a black win or a draw")}

>>>>

```{r, label=loadlibrary}
library("hyper2")

@@

```{r,label=specplay}
  players <- 
    c("Petrosian", "Keres", "Geller", "Fischer", "Korchnoi",
      "Benko", "Tal", "Filip")
  names(players) <-   # accused of collusion or not
    c("coll", "coll", "coll", "USA", "USSR", "USA", "USSR", "TCH")
collusive_players <-     c("Petrosian", "Keres", "Geller")
```

@@

```{r cumandcons}
cumulative_games
cumulative_collusive_games
cumulative_noncollusive_games
```

@@

```{r calcdiff}
diff <- a$cncmp_white-a$cncmp_black  # difference in each game
table(diff)
table(abs(diff))
cumsum(table(abs(diff)))
```

@@

```{r assessnullnofat}
table(a[,3],a[,5]-a[,6])
```

Then Fisher test:
```{r thenfish}
b <- subset(a,a[,5] != a[,6])
b <- subset(b,abs(b[,5]-b[,6])>1)
b <- subset(b,b[,3] != "1/2-1/2")
b <- cbind(b,white_rested = b[,5] < b[,6])
b

@@

```{r hyper2reified}
problem <- function(...){stop("must be a white win or a black win or a draw")}
